The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-11-05 outputs/docs/events/paper.Rmd
Add graph of missing dates for Appendix A

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: changes in government tend be associated with topic changes even when the party in power does not change; elections that do not result in a change in government are rarely associated with topic changes; economic events, such as financial crises, have less significant effects than other events such as terrorist attacks; and the effect of events is much more pronounced in the second half of our sample, and especially in the past two decades. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
keywords: "text, politics, Australia, unsupervised machine learning, Bayesian model."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

We systematically analyse the text using two main statistical techniques. To reduce the dimensionality of our dataset we use a topic model that allows correlation between topics. We then analyse the topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events. These events include: changes in government; elections; and other significant events such as an economic recession or terrorism.

@@

```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics("../../figures/topics_example.pdf")
```

@@

## Known Hansard issues {#knownhansardissues}
Comparing the sitting days to the dates that we have suggests some issues with the dataset (Table \@ref(tab:missingdays)).)

@@

Add the graphs and procedures.

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, and the Parliamentary Library. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: changes in government tend be associated with topic changes even when the party in power does not change; elections that do not result in a change in government are rarely associated with topic changes; economic events, such as financial crises, have less significant effects than other events such as terrorist attacks; and the effect of events is much more pronounced in the second half of our sample, and especially in the past two decades. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
keywords: "text, politics, Australia, unsupervised machine learning, Bayesian model."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

We systematically analyse the text using two main statistical techniques. To reduce the dimensionality of our dataset we first use a topic model that allows correlation between topics. We then analyse those topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events. These events include: changes in government; elections; and other significant events such as an economic recession or terrorism.

@@

```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
# knitr::include_graphics("../../figures/topics_example.pdf")
```

@@

## Summary statistics

```{r countsbyyear, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '90%'}
knitr::include_graphics("../../figures/counts_by_year.pdf")
```

## Compared with parliamentary website {#knownhansardissues}
Comparing the sitting days to the dates that we have suggests some issues with the dataset (Table \@ref(tab:missingdays)).)

@@

Add the graphs and procedures. **[TBD]**

### 2018-11-05 outputs/docs/events/slides/slides.Rmd
Add graph of missing dates for Appendix A

---
title: The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)
subtitle: 
author:
- Monica Alexander, University of Toronto\newline
- Rohan Alexander, Australian National University
date: 24 October 2018
institute: Presentation at the School of Politics and International Relations, Australian National University, Canberra, Australia.
output: binb::metropolis
# output: ioslides_presentation
fontsize: 12pt
---

@@

key_events_results <- read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols())

@@

## Hansard
- A daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901. It's not vertatim, but it's pretty close.
- Hansard records have been used in other counties but not really at scale in Australia (although others are also starting to use them).
- Daily PDFs are available Hansard records available online as PDFs and these are considered the official release. 
- There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.

@@

```{r pressureFig, echo=FALSE, out.width = '50%', fig.align="center"}

@@

```{r exampletopics, cache = TRUE, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../../../figures/topics_example-slides.pdf")
```

@@

## Analysis model - Daily distribution
The topic proportions on day $d$ are modelled in reference to their membership of a particular sitting period $s$. Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:

$$
\theta_{d,1:P} \sim \mbox{Dirichlet}(\mu_{s[d],1:P})
$$

@@

```{r wartopicsgraph, cache = TRUE, echo = FALSE, out.width = '100%'}
knitr::include_graphics("../../../figures/war_stack.pdf")
```

@@

```{r mugov, cache = TRUE, echo = FALSE, out.width = '100%'}
knitr::include_graphics("../../../figures/mu_gov.pdf")
```

@@

```{r muelection, cache = TRUE, echo = FALSE, out.width = '100%'}
knitr::include_graphics("../../../figures/mu_election.pdf")
```

@@

key_events_results %>%
  kable(caption = "Days that were significantly different to other days in their sitting period") %>%
  kable_styling(font_size = 10)

@@

## Whitlam stability

@@

# Future work

## Future work
- Group identity: which is more important?
-

@@

>>>>

---
title: The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)
subtitle: 
author:
- Monica Alexander, University of Toronto\newline
- Rohan Alexander, Australian National University
date: 25 October 2018
institute: Presentation at the Research School of Economics, Australian National University, Canberra, Australia.
output: binb::metropolis
# output: ioslides_presentation
fontsize: 12pt
---

@@

key_events_results <- read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols())
#breka
```

@@

## Hansard
- A daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901. It's not vertatim, but it's pretty close.
- Hansard records have been used in other counties but not really at scale in Australia (although others, such as Patrick Leslie, also use them).
- Daily PDFs are available Hansard records available online as PDFs and these are considered the official release. 
- There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.

@@

```{r pressureFig, echo=FALSE, out.width = '75%', fig.align="center"}

@@

```{r exampletopics, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../../../figures/topics_example-slides.png")
```

@@

## Analysis model - Daily distribution
The topic proportions on day $d$ are modelled in reference to their membership of a particular sitting period $s$. Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
$$
\theta_{d,1:P} \sim \mbox{Dirichlet}(\mu_{s[d],1:P})
$$

@@

```{r wartopicsgraph, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
knitr::include_graphics("../../../figures/war_stack-slides.pdf")
```

@@

```{r mugov, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
knitr::include_graphics("../../../figures/mu_gov-slides.pdf")
```

@@

```{r muelection, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
knitr::include_graphics("../../../figures/mu_election-slides.pdf")
```

@@

key_events_results %>%
  kable() %>%
  kable_styling(font_size = 10)
#CAS
```

@@

## Whitlam re-election

@@

# Current/future work

## Current/future work
<!-- ### Improve data -->
<!-- - Trying to get website data instead of needing to parse PDFs. -->

### Current work
- In-group and out-group identity: which is more important?
- Senate/HoR: just how different are they?
- Methods assessment: how is your cleaning impacting your results?
- States/Commonwealth: where does policy come from?

### Future
- Open to suggestions and keen for collaboration.

@@

```{r hansardphoto, echo=FALSE, out.width = '75%', fig.align="center"}

knitr::include_graphics("../../../figures/hansard_photo.png")
